---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis build status](https://travis-ci.org/katiejolly/advicegiveR.svg?branch=master)](https://travis-ci.org/katiejolly/advicegiveR)

# advicegiveR

The goal of advicegiveR is to provide an easy way to make calls to the [advice slip API](http://api.adviceslip.com/). It also provides a fun way to share the advice you get!

## Installation

You can install advicegiveR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("katiejolly/advicegiveR")
library(advicegiveR)
```

## Examples

```{r include = FALSE}
library(advicegiveR)
```


Get a random piece of advice:

```{r}
get_advice()
```

The advice slip API has 216 different outputs (from what I can tell). You can also request a particular piece of advice using the `id` argument. If you get a random piece of advice, the function will tell you what `id` it ended up using so you can find it again. 

```{r}
advice <- get_advice(id = 25)

advice
```

Then if you want to print the advice on an image, I have some images ready for you! You can choose from `clouds`, `mountain`, `ocean`, `paper`, `sunset`, or `rainbow`. (You can also use your own image loaded with the `magick` package.)

```{r}
mountain <- load_image(image_name = "mountain")
```

After you've chosen your image, you can put the advice and image together.

```{r image}
print_advice(image = mountain, advice = advice, textcolor = "yellow", size = 40)
```

Then you can save the image you created! A good way comes from the `magick` package:

```{r eval=FALSE}
magick::image_write(...)
```

## Contributing

If you have an idea for this package, feel free to submit an issue or pull request! 
